Generate data for multispecies modeling, including diet!

### 2020-09-17 NOBAmsdiets.Rmd
omdimensions is wrong problem found still needs fix

```{r, code = readLines("./config/NOBA2Config.R")}
```

@@

```{r, code = readLines("./config/omdimensions.R")}
```

@@

```{r, code = readLines("./config/mssurvey_spring.R")}
```

```{r, code = readLines("./config/mssurvey_fall.R")}
```

@@

```{r, code = readLines("./config/msfishery.R")}
```

@@

#read time series data--now needs survey name from config files
survname <- c("BTS_spring_allbox_effic1", "BTS_fall_allbox_effic1")

@@

survObsBiom <- NOBAom_ms$survObsBiom[[survname]]

plotB <-ggplot() +
  geom_line(data=survObsBiom, aes(x=time/stepperyr,y=atoutput, color="survey Biomass"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotB +
  facet_wrap(~species, scales="free")

>>>>

```{r, code = readLines("./config/NOBA2Config.R"), eval=F}
```

@@

```{r, code = readLines("./config/omdimensions.R"), eval=F}
```

@@

```{r, code = readLines("./config/mssurvey_spring.R"), eval=F}
```

```{r, code = readLines("./config/mssurvey_fall.R"), eval=F}
```

@@

```{r, code = readLines("./config/msfishery.R"), eval=F}
```

@@

#read time series data--now needs survey name from config files

@@

survObsBiom <- NOBAom_ms_ind$survObsBiom

plotB <- function(dat){

    ggplot() +
    geom_line(data=dat, aes(x=time/stepperyr,y=atoutput, color="survey Biomass"), 
              alpha = 10/10) +
    theme_tufte() +
    theme(legend.position = "top") +
    labs(colour=scenario.name) +
    facet_wrap(~species, scales="free")

}

# why is herring missing from both?
herring <- NOBAom_ms$truebio_ss %>%
  filter(species %in% c("Norwegian_ssh")) %>%
  group_by(species, time) %>%
  summarise(totB = sum(atoutput))

# problem--omdimensions is doing species age accounting wrong
# species alphabetical pulled separately but ages not
# pull species name, n age classes and n ages all at once to avoid bad sorting
```

##### `r names(survObsBiom)[1]`
``` {r}
map(survObsBiom$BTS_spring_allbox_effic1, plotB)[[1]]
```

##### `r names(survObsBiom)[2]`
```{r}
map(survObsBiom$BTS_fall_allbox_effic1, plotB)[[1]]
```
